### 2020-08-31 thesis/chap_2.tex
add line
fix naming

Conservation status determines whether or not forest can be cut down, and whether pixels can transition into urban and agricultural land. In Chapter 1, we gave this status to areas that were previously known as protected, but assumed no more forest would be added to this set of protected areas. In this chapter, a protection status is given to all pixels within the identified priority areas and within a 5km buffer around the identified priority linkage areas. All pixels under this status cannot transition into urban land and remain in their state. This represents an unrealistic proportion of the region under protection (about 33% of the region)

@@

The three modified conservation and land use change scenarios are therefore:
\begin{enumerate}
  \item Business as usual land use change + corridor protection \textbf{(BAU-Corr)}
 \item Business as usual land use change + corridor protection + reforestation \textbf{(BAU-R-Corr)}
 \item Business as usual land use change + corridor protection + targeted reforestation \textbf{(BAU-R(T)-Corr)} \\
\end{enumerate}

@@

The information contained in those maps is summarized with a bar chart showing changes in Agricultural, Urban and Forested land use area for 2010 and 2100 (see figure \ref{fig:bar_chap2}). For all scenarios, the urban area was allowed to almost double. This is apparent in all maps, where urban land has spread in a similar fashion to the BAU scenario in Chapter 1. Forest is maintained for all scenarios except for the BAU-Corr scenario, which only differs from the BAU scenario of chapter 1 in that the links and areas identified by stakeholders are protected from urbanization and agricultural expansion. In this scenario, agriculture is also allowed to maintain its area. This is not the case for the other scenarios, which include reforestation, which, in the context of spreading urban land, must result in the loss in agricultural land (similarly to what was observed under the reforestation scenario in Chapter 1).

Although the two conservation scenarios that include reforestation do not differ in their changes to the different land use area, they display different spatial patterns. Under the BAU-R-Corr scenario we observe a similar pattern of growing forest patches than under Chapter 1's Reforestation scenario : small patches have disappeared (except in the corridors) and bigger patches have grown. But we see the most striking difference with the last conservation scenario, BAU-R(T)-Corr, for which reforestation is targeted to the corridors identified by the stakeholders. Under this scenario, we still assume that forests grow from existing patches. The consequence of these two constraints is that where forest can grow easily in a linear fashion, it tends to do so. Therefore we see that corridors of forest are delineated, within the 5km buffer around identified links that were given to the model. The pattern is especially striking in the north of the region. In the south and the west of the region, we see a different pattern under which the model generated the growth of the identified forested cores. \\

@@

We can note the variations on which of the two reforestation scenarios is most effective at curbing the decrease in mean flow, the degree of which tends to depend on the climate scenario as well as the species. For the wood frog, random reforestation performs better than targeted reforestation, invariant on climate. Same pattern for the red-backed salamander, but for it warming scenarios are consistently better and lead to less loss in mean flow. For the back bear, the two reforestation scenarios ended with the same amount of loss in 2100 (despite some early divergence), and did not depend on the climate scenario. The flow values for the short-tailed shrew also decrease less under the random reforestation scenario, and displays larger differences between historic and climate change scenarios. Finally, the most complex patterns are observed for the american marten. Although it also seems to do better under random reforestation, the response varies with the climate scenario; the response curves are staggered in such a way that targeted reforestation under the baseline climate scenario predicted higher mean flow than random reforestation under RCP 8.5. Similarly, the BAU scenario under baseline climate predicts higher flow values than the BAU-Corr scenario under RCP 8.5. This highlights an apparent non-linear response to climate by the american marten, for which baseline climate seems worse than RCP 8.5 but better than historical change.

@@

In the conservation scenarios of this chapter we see that the BAU-Corr scenario has a clear directional effect across all species' histograms (see figure \ref{fig:hist_2}) toward smaller flow values, whereas the other two scenarios which include reforestation have a polarizing effect, similarly to in Chapter 1. However, in the case of the black bear, we see a directional shift toward more positive values.

@@

Similar limitations to those raised in chapter 1 also apply. For instance, the habitat suitability analysis, and the analysis of flow surfaces have important flaws that would need to be addressed (see chapter 1 for more details). Another critique could be made about the targeted reforestation scenario: due to the parameterization of the reforestation, it was easier for patches in the north of the region to grow into linear strips of corridors. This happened at a lower rate in the southern part of the region, due to the lack of the pre-existing patches of forest. Future scenarios will need to test if allowing for new patches to spawn on the map produces the same outputs - as long as this land use change trend is thought likely by stakeholders.

>>>>

Conservation status determines whether or not forest can be cut down, and whether pixels can transition into urban and agricultural land. In Chapter 1, we gave this status to areas that were previously known as protected, but assumed no more forest would be added to this set of protected areas. In this chapter, a protection status is given to all pixels within the identified priority areas and within a 5km buffer around the identified priority linkage areas. All pixels under this status cannot transition into urban land and remain in their state. This represents an unrealistic proportion of the region under protection (about 33\% of the region).

@@

The three modified conservation and land use change scenarios are therefore:
\begin{enumerate}
  \item Business as usual land use change + corridor protection \textbf{(CorPr)}
 \item Business as usual land use change + corridor protection + reforestation \textbf{(R-CorPr)}
 \item Business as usual land use change + corridor protection + targeted reforestation \textbf{(R(T)-CorPr)} \\
\end{enumerate}

@@

The information contained in those maps is summarized with a bar chart showing changes in Agricultural, Urban and Forested land use area for 2010 and 2100 (see figure \ref{fig:bar_chap2}). For all scenarios, the urban area was allowed to almost double. This is apparent in all maps, where urban land has spread in a similar fashion to the BAU scenario in Chapter 1. Forest is maintained for all scenarios except for the CorPr scenario, which only differs from the BAU scenario of chapter 1 in that the links and areas identified by stakeholders are protected from urbanization and agricultural expansion. In this scenario, agriculture is also allowed to maintain its area. This is not the case for the other scenarios, which include reforestation, which, in the context of spreading urban land, must result in the loss in agricultural land (similarly to what was observed under the reforestation scenario in Chapter 1).

Although the two conservation scenarios that include reforestation do not differ in their changes to the different land use area, they display different spatial patterns. Under the R-CorPr scenario we observe a similar pattern of growing forest patches than under Chapter 1's Reforestation scenario : small patches have disappeared (except in the corridors) and bigger patches have grown. But we see the most striking difference with the last conservation scenario, R(T)-CorPr, for which reforestation is targeted to the corridors identified by the stakeholders. Under this scenario, we still assume that forests grow from existing patches. The consequence of these two constraints is that where forest can grow easily in a linear fashion, it tends to do so. Therefore we see that corridors of forest are delineated, within the 5km buffer around identified links that were given to the model. The pattern is especially striking in the north of the region. In the south and the west of the region, we see a different pattern under which the model generated the growth of the identified forested cores. \\

@@

We can note the variations on which of the two reforestation scenarios is most effective at curbing the decrease in mean flow, the degree of which tends to depend on the climate scenario as well as the species. For the wood frog, random reforestation performs better than targeted reforestation, invariant on climate. Same pattern for the red-backed salamander, but for it warming scenarios are consistently better and lead to less loss in mean flow. For the back bear, the two reforestation scenarios ended with the same amount of loss in 2100 (despite some early divergence), and did not depend on the climate scenario. The flow values for the short-tailed shrew also decrease less under the random reforestation scenario, and displays larger differences between historic and climate change scenarios. Finally, the most complex patterns are observed for the american marten. Although it also seems to do better under random reforestation, the response varies with the climate scenario; the response curves are staggered in such a way that targeted reforestation under the baseline climate scenario predicted higher mean flow than random reforestation under RCP 8.5. Similarly, the BAU scenario under baseline climate predicts higher flow values than the CorPr scenario under RCP 8.5. This highlights an apparent non-linear response to climate by the american marten, for which baseline climate seems worse than RCP 8.5 but better than historical change.

@@

In the conservation scenarios of this chapter we see that the CorPr scenario has a clear directional effect across all species' histograms (see figure \ref{fig:hist_2}) toward smaller flow values, whereas the other two scenarios which include reforestation have a polarizing effect, similarly to in Chapter 1. However, in the case of the black bear, we see a directional shift toward more positive values.

@@

Similar limitations to those raised in chapter 1 also apply. For instance, the habitat suitability analysis, and the analysis of flow surfaces have important flaws that would need to be addressed (see chapter 1 for more details). Another critique could be made about the targeted reforestation scenario: due to the parameterization of the reforestation, it was easier for patches in the north of the region to grow into linear strips of corridors. This happened at a lower rate in the southern part of the region, due to the lack of the pre-existing patches of forest. Future scenarios will need to test if allowing for new patches to spawn on the map produces the same outputs - as long as this land use change trend is thought likely by stakeholders. \\
